---
title: "Example for Replicate One"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE , message = FALSE)
```


```{r read_in , echo = FALSE}
### install.packages(dplyr)
### install.package(ggplot2)
library(dplyr)
library(ggplot2)
nms = paste0("X", seq(1,13,1))
Matrices = readr::read_csv("Liquid Assay Data for R (Including Outliers).csv",
                           col_names = FALSE ) %>%
  purrr::set_names(nms)
CreateSplites = Matrices %>%
  mutate(ReplicateInd = ifelse(!is.na(X13) , paste0("REP",row_number() ), NA)) %>%
  tidyr::fill(ReplicateInd, .direction = "down") %>%
  filter(!is.na(X1)) %>%
  split(.$ReplicateInd)
Indice = as.list( seq(1, length(CreateSplites),1) )
```

```{r get_control, echo = FALSE}
Scalar = CreateSplites[[1]] %>%
  select(13) %>%
  filter(row_number() == 1) %>%
  pull(X13)
```

**The scalar is `r Scalar` from replicate one. **

```{r before_control , echo = FALSE}
gt::gt(CreateSplites[[1]] %>% 
         mutate_if(is.numeric, ~round(. , digits = 4))) %>% 
   gt::tab_options(
    table.font.size = 12
  )
```



```{css, echo=FALSE}
.watch-out {
  background-color: lightpink;
  border: 3px solid red;
  font-weight: bold;
}
```




**This code divides all columns and rows by the scalar, `r Scalar`:**



```{r class.source="watch-out"}
Matrices2 = CreateSplites[[1]] %>%
  select(1:12) %>%
  mutate_all(funs(./Scalar))
```  

```{r after_control, echo = FALSE}
gt::gt(Matrices2 %>% 
         mutate_if(is.numeric, ~round(. , digits = 4))) %>% 
   gt::tab_options(
    table.font.size = 12
  )
```


```{r diagonals, echo = FALSE}
Matrices3 = Matrices2 %>%
  purrr::set_names(LETTERS[1:12]) %>%
  mutate(RowNms = LETTERS[1:12]) %>%
  tidyr::gather(Key, value, -RowNms)
  
  
Diagonal_a = Matrices2 %>%
  as.matrix(.) %>%
  diag()
  
FullGrid = expand.grid(LETTERS[1:12], LETTERS[1:12])
Diagonal = tibble(Letters = LETTERS[1:12], val = Diagonal_a)
  
Products = FullGrid %>%
  inner_join(Diagonal , by = c("Var1" = "Letters") ) %>%
  inner_join(Diagonal , by = c("Var2" = "Letters") ) %>%
  filter(Var1 != Var2) %>%
  mutate(DiagonalProducts = val.x * val.y) %>%
  inner_join(Matrices3 , by = c("Var1"="RowNms", "Var2" = "Key")) %>%
  mutate(ReplicateNumber = paste0("Replicate-",1))
  
